INTELLIGENT SYSTEMS

### 2021-04-07 paper_5.tex
finish 5.4.1

\subsubsection{Identity Authentication}

>>>>

\subsubsection{Identity Authentication}
An authentication process begins by submitting a sample of input to CNN. 
Within this, there may be a layer that will produce a vector of features. 
To find out which layer it is, a cross-validation process is performed. Once 
extracted, the features are normalized with the L2 standard. Subsequently 
a vector is calculated containing the Euclidean distances between the values 
given in input and those present in the training set. In order to calculate the 
\emph{Area Under Curve} (AUC) or the \emph{Equal-Error-Rate} (EER), these distances 
are transformed into probabilities.

\subsection{EXPERIMENTS AND RESULTS}
\subsubsection{Dataset}
The OU-ISIR dataset is composed in two parts. Part A contains data on 744 
individuals, each having two sub-sequence (s) recording at a rate of 100Hz 
via an IMU sensor located at the waist of each. The first sequence is used for 
training, the second for testing. The labels associated with each individual 
are: identity, gender and age (split in ranges). Part B, on the other hand, 
is composed of 495 individuals with 3 IMU sensors located on the body. For 
each individual and sensor, there are two sequences of walking levels, an up-slope 
walk sequence and the other down-slope walk. The data that will be 
merged are those coming from sensors such as accelerometer and gyroscope.
